\textbf{Volatility and the Buyback Anomaly: Online Interactive Tool Report}

### 2016-05-17 toolreport.Rnw
errors
some data code
typos

\vspace{-.2in}
\begin{abstract}
\noindent This is a customized report of the online interactive tool for the paper "{\it Volatility and the Buyback Anomaly}" by T. Evgeniou, Enric Junqu\'e de Fortuny, Nick Nassuphis, and Theo Vermaelen.

\end{abstract}
\vspace{2cm}

@@

The time period used in this report is from \Sexpr{startdate} to \Sexpr{enddate}. We only consider firms with a market capitalization the month before the event being between \Sexpr{market_cap_min} and \Sexpr{market_cap_max}. In addition to the financial and utilities sectors, we also remove the following sectors: \Sexpr{paste(industry, collapse=", ")}. This leaves a total of \Sexpr{length(DATASET_NEW$value.weights)} buyback events.

@@

Ww consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the quantiles of events defined using the selected event characteristic, namely \Sexpr{gsub("\\.", " ", characteristic_single_analysis)}. Table \ref{tbl:indcharacteristic} shows the results. Figure \ref{fig:indcharacteristic} shows the excess returns of a strategy for that trades only the high or low quantile stocks for this event characteristics (the strategy is designed as described in the paper). Table \ref{tbl:indcharacteristicpnl} shows the monthly and yearly returns of the "high" events strategy.

@@

We define a customized Undervaluation index using the following event characteristics: \Sexpr{gsub("\\.", " ", characteristic_irats1)} (sign is \Sexpr{ifelse(characteristic_irats1_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats2)} (sign is \Sexpr{ifelse(characteristic_irats2_sign, -1, +1)}),\Sexpr{gsub("\\.", " ", characteristic_irats3)} (sign is \Sexpr{ifelse(characteristic_irats3_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats4)} (sign is \Sexpr{ifelse(characteristic_irats4_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats5)} (sign is \Sexpr{ifelse(characteristic_irats5_sign, -1, +1)}), \Sexpr{gsub("\\.", " ", characteristic_irats6)} (sign is \Sexpr{ifelse(characteristic_irats6_sign, -1, +1)}). For each of these characteristics we define the high and low events as those that are in the top or bottom \Sexpr{100*quantile_used_ind}$\%$ of the events. We then assign a score of 2 for the high, 0 for the low, and 1 for the rest of the events for each of these characteristics, and we add up these scores to create the customized undervaluation index. Figure \ref{fig:undervaluationindex} shows the number of events for each of the values of this customized index.

We then consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the quantiles of events defined using this customized Undervaluation Index. Table \ref{tbl:CUcharacteristic} shows the results. Figure \ref{fig:CUcharacteristic} shows the excess returns of a strategy for that trades only the high or low quantile stocks for this customized undervaluation index (the strategy is designed as described in the paper). Table \ref{tbl:CUcharacteristicpnl} shows the monthly and yearly returns of the "high" events strategy.

>>>>

\vspace{-.2in}
\begin{abstract}
\noindent This is a customized report of the online interactive tool for the paper {\it ``Volatility and the Buyback Anomaly''} by T. Evgeniou, Enric Junqu\'e de Fortuny, Nick Nassuphis, and Theo Vermaelen.

There is no guarantee that there is no error in all possible customized reports.

\end{abstract}
%\vspace{2cm}

@@

The time period used in this report is from \Sexpr{startdate} to \Sexpr{enddate}. We only consider firms with a market capitalization the month before the event being between \Sexpr{market_cap_min} and \Sexpr{market_cap_max}. In addition to the financial and utilities sectors, we also remove the following sectors: \Sexpr{ifelse(length(industry) == 0, "None", paste(industry, collapse=", "))}. This leaves a total of \Sexpr{length(DATASET_NEW$value.weights)} buyback events.

@@

We consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the high and low quantiles of events defined using the selected event characteristic, namely \Sexpr{gsub("\\.", " ", characteristic_single_analysis)}. Table \ref{tbl:indcharacteristic} shows the results. Figure \ref{fig:indcharacteristic} shows the excess returns of a strategy  that trades only the high or low quantile stocks for this event characteristic (the strategy is designed as described in the paper). Table \ref{tbl:indcharacteristicpnl} shows the monthly and yearly returns of the high quantile events strategy.

@@

We define a customized Undervaluation index using the following event characteristics: \Sexpr{ifelse(characteristic_irats1 != "None",  paste(gsub("\\.", " ", characteristic_irats1), " (sign is ", ifelse(characteristic_irats1_sign, "-1","+1"),")",sep = ""), " ") } \Sexpr{ifelse(characteristic_irats2 != "None",  paste(",", gsub("\\.", " ", characteristic_irats2), " (sign is ", ifelse(characteristic_irats2_sign, "-1","+1"),")",collapse = ""), " ") }  \Sexpr{ifelse(characteristic_irats3 != "None",  paste(",", gsub("\\.", " ", characteristic_irats3), " (sign is ", ifelse(characteristic_irats3_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats4 != "None",  paste(",", gsub("\\.", " ", characteristic_irats4), " (sign is ", ifelse(characteristic_irats4_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats5 != "None",  paste(",", gsub("\\.", " ", characteristic_irats5), " (sign is ", ifelse(characteristic_irats5_sign, "-1","+1"),")",collapse = ""), " ") } \Sexpr{ifelse(characteristic_irats6 != "None",  paste(",", gsub("\\.", " ", characteristic_irats6), " (sign is ", ifelse(characteristic_irats6_sign, "-1","+1"),")",collapse = ""), " ") }. For each of these characteristics we define the high and low events as those that are in the top or bottom \Sexpr{100*quantile_used_ind}$\%$ of the events. We then assign a score of 2 for the high, 0 for the low, and 1 for the rest of the events for each of these characteristics, and we add up these scores to create the customized undervaluation index. Figure \ref{fig:undervaluationindex} shows the number of events for each of the values of this customized index.

We then consider the IRATS Cumulative Abnormal Returns (CAR) and Calendar Time method Abnormal Returns (AR) of the high/low quantiles of events defined using this customized Undervaluation Index. Table \ref{tbl:CUcharacteristic} shows the results. Figure \ref{fig:CUcharacteristic} shows the excess returns of a strategy that trades only the high or low quantile stocks for this customized undervaluation index (the strategy is designed as described in the paper). Table \ref{tbl:CUcharacteristicpnl} shows the monthly and yearly returns of the high quantile events strategy.
